\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
rewrite of section 3 including improvement to MinT section

Note here that we rely here on the Generalised Pythagorean Theorem (which involves an equality). In contrast, \citet{WicEtAl2019} follow \citet{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality. The proof of \citet{WicEtAl2019} requires an assumption of convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees. The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$. As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only with respect to a loss function that depends on {\color{blue} $||.||_{\bm{W}^{-1}}$ and only when $\bm{W}$ is the covariance matrix estimate used by MinT}. If Euclidean distance (or mean squared error) is used {\color{blue} as a loss function}, there will be realisations where the MinT estimator does not improve forecast accuracy relative to base forecasts. This will be demonstrated using a real data set in the empirical study in Section~\ref{sec:comparebase}.

@@

{\color{blue}The discussion so far provides a roadmap, such that for a given choice of $\bm{W}$, a projection method with distance-reducing properties can be derived}. While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different optimality property of minimising the} trace of the forecast error covariance matrix of reconciled forecasts

@@

\subsection{MinT and Loss Functions}

We now make explicit the connection betwenn the MinT and a loss function based on the Euclidean distance $L(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|$.  By the properties of the trace operator, the objective function in Equation~\ref{eq:MinTObj} can be rearranged as

@@

Note that although the loss function used here is the same as in Section~\ref{sec:orthogonal}, the sense in which reconciliation is optimal is different.  Theorem~\ref{th:distred} implies optimality in the sense that reconcilied forecasts always improve on base forecasts.  For MinT, optimality refers to minimising the expected loss function \textit{in expectation}.

A natural question may be to derive a reconciliation method that minimises expected loss where the loss function is the generalised Euclidean distance between the realisation and reconciled forecast.  That is to solve the optimisation problem

{\color{blue}
	\begin{equation}
	\label{eq:GMinTObj}
	\underset{\bm{G}}{\min}\,\textrm{tr}(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'\bm{W}^{-1}(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})\right])\,.
	\end{equation}
}

@@

\begin{theo}[MinT minimises expected loss]\label{th:gdistred}
    The usual MinT reconciliation method $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}$ solves the optimisation problem in Equation~\ref{eq:GMinTObj} for any $\bm{W}$.
\end{theo}
\begin{proof}
	The loss function in Equation~\ref{eq:GMinTObj} is equivalent to Euclidean distance in the transformed space and can therefore be minimised by using the MinT method in this space.  The MinT method in the transformed space is give by 
	\begin{equation}
	\label{eq:MinTtran}
	\tilde{\bm{y}}^{*}=\bm{S}^{*}\left(\bm{S}^{*'}\bm{\Sigma}^{*-1}\bm{S}^{*}\right)^{-1}\bm{S}^{*'}\bm{\Sigma}^{*-1}\hat{\bm{y}}^{*}\,,
	\end{equation}
	where  $\bm{y}^{*}=\bm{W}^{-1/2}\bm{y}$, $\bm{S}^{*}=\bm{W}^{-1/2}\bm{S}$, $\hat{\bm{y}}^{*}=\bm{W}^{-1/2}\hat{\bm{y}}$ and
	\begin{align*}
	\bm{\Sigma}^*&=E\left[(\bm{y}^{*}-\hat{\bm{y}}^{*})(\bm{y}^{*}-\hat{\bm{y}}^{*})'\right]\\
	&=E\left[\bm{W}^{-1/2}(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'\bm{W}^{-1/2'}\right]\\
	&=\bm{W}^{-1/2}E\left[(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'\right]\bm{W}^{-1/2'}\\
	&=\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'}
	\end{align*}
	Substituting the expressions for $\bm{\Sigma}^*$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Equation~\ref{eq:MinTtran} yields, 
	\begin{align*}
	\bm{W}^{-1/2}\tilde{\bm{y}}=\bm{W}^{-1/2}\bm{S}&\left((\bm{W}^{-1/2}\bm{S})'(\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'})^{*-1}\bm{W}^{-1/2}\bm{S}\right)^{-1}\\
	&(\bm{W}^{-1/2}\bm{S})'(\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'})^{*-1}\bm{W}^{-1/2}\hat{\bm{y}}
	\end{align*}
	Rearranging and cancelling gives
	\begin{align*}
    \tilde{\bm{y}}&=\bm{S}\left((\bm{S})'(\bm{W}^{-1/2})'(\bm{W}^{1/2})'\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\bm{S}\right)^{-1}\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2})'\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\hat{\bm{y}}\\
	&=\bm{S}\left((\bm{S})'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}\\
	\end{align*}
	which corresponds to the usual MinT method.
\end{proof}

>>>>

\citet{WicEtAl2019} and \citet{VanErven2015a} both prove special cases of this result, the former in the case where $\bm{W}$ is the inverse of the forecast error covariance and \citet{VanErven2015a} in the case where $\bm{W}$ is diagonal.  Note here that we rely here on the Generalised Pythagorean Theorem (which involves an equality). In contrast, \citet{WicEtAl2019} follow \citet{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality. These proofs require an assumption of convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees. The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$. As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only with respect to a loss function that depends on {\color{blue} $||.||_{\bm{W}}$ and only when $\bm{W}^{-1}$ is the covariance matrix estimate used by MinT}. If Euclidean distance (or mean squared error) is used {\color{blue} as a loss function}, there will be realisations where the MinT estimator does not improve forecast accuracy relative to base forecasts. This will be demonstrated using a real data set in the empirical study in Section~\ref{sec:comparebase}.

@@

{\color{blue}The discussion so far provides a roadmap, such that for a given choice of $\bm{W}$, a projection method with distance-reducing properties can be derived}. While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different optimality property.  This was to minimise the} trace of the forecast error covariance matrix of reconciled forecasts

@@

\subsection{Expected loss minimisation and MinT}

We now make explicit the connection betwenn the MinT and a loss function based on the Euclidean distance $L(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|$ before generalising to $L_{\bm W}(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|_{\bm W}$.  By the properties of the trace operator, the objective function in Equation~\ref{eq:MinTObj} can be rearranged as

@@

Note that although the loss function used here is the same as in Section~\ref{sec:orthogonal}, the sense in which reconciliation is optimal is different.  Theorem~\ref{th:distred} implies optimality in the sense that reconcilied forecasts always improve on base forecasts.  For MinT, optimality refers to minimising the loss function \textit{in expectation}.

Suppose the optimisation problem is generalised to a loss function based on some ${\bm W}$

{\color{blue}
	\begin{equation}
	\label{eq:GMinTObj}
	\underset{\bm{G}}{\min}\,(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'\bm{W}(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})\right])\,.
	\end{equation}
}

@@

\begin{theo}[Expected loss minimisation and MinT]\label{th:gdistred}
    The usual MinT reconciliation method $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}$ solves the optimisation problem in Equation~\ref{eq:GMinTObj} for any choice of $\bm{W}$.
\end{theo}
\begin{proof}
	The loss function in Equation~\ref{eq:GMinTObj} is equivalent to Euclidean distance in the transformed space and can therefore be minimised by using the MinT method in this space.  The MinT method in the transformed space is given by 
	\begin{equation}
	\label{eq:MinTtran}
	\tilde{\bm{y}}^{*}=\bm{S}^{*}\left(\bm{S}^{*'}\bm{\Sigma}^{*-1}\bm{S}^{*}\right)^{-1}\bm{S}^{*'}\bm{\Sigma}^{*-1}\hat{\bm{y}}^{*}\,,
	\end{equation}
	where  $\bm{y}^{*}=\bm{W}^{1/2}\bm{y}$, $\bm{S}^{*}=\bm{W}^{1/2}\bm{S}$, $\hat{\bm{y}}^{*}=\bm{W}^{1/2}\hat{\bm{y}}$ and
	\begin{align*}
	\bm{\Sigma}^*&=E\left[(\bm{y}^{*}-\hat{\bm{y}}^{*})(\bm{y}^{*}-\hat{\bm{y}}^{*})'\right]\\
	&=E\left[\bm{W}^{1/2}(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'(\bm{W}^{1/2})'\right]\\
	&=\bm{W}^{1/2}E\left[(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'\right](\bm{W}^{1/2})'\\
	&=\bm{W}^{1/2}\bm{\Sigma}(\bm{W}^{1/2})'
	\end{align*}
	Noting that
	\begin{align*}
	(\bm{\Sigma}^{*})^{-1}&=\left(\bm{W}^{1/2}\bm{\Sigma}(\bm{W}^{1/2})'\right)^{-1}\\
	&=(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\\
	\end{align*}
	and substituting the expressions for $\bm{\Sigma}^*$,${\bm{S}^*}$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Equation~\ref{eq:MinTtran} yields, 
	\begin{align*}
	\bm{W}^{1/2}\tilde{\bm{y}}=\bm{W}^{1/2}\bm{S}&\left((\bm{W}^{1/2}\bm{S})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}(\bm{W}^{1/2}\bm{S})\right)^{-1}\\
	&(\bm{W}^{1/2}\bm{S})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\hat{\bm{y}}
	\end{align*}
	Rearranging and cancelling gives
	\begin{align*}
    \tilde{\bm{y}}&=\bm{S}\left(\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\bm{S}\right)^{-1}\\
    &\qquad\qquad\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\hat{\bm{y}}\\
	&=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}\\
	\end{align*}
	which corresponds to the usual MinT method.
\end{proof}

The implication of this result is that irrespective of the ${\bm W}$ used in the loss function, an oblique projection based on the forecast error covariance will always minimise {\em expected} loss (for the class of loss functions considered here).  From the point of view of minimising expected loss, considerations about sensible weights for an error metric will only work in so far as they can estimate the forecast error covariance matrix.  This will be empirically demonstrated in Section~\ref{sec:EmpStudy}.
